## data cleaning
# Data transformation

## Question1: Analyze the development process of U.S. export data

### Overall trend in data of exports of goods and services

Transformation of overall data of US exports of goods and services
```{r}
library(tidyverse)
library(readxl)
overall_data_exports_goods_services<-read_excel(here::here("IEAXGS.xls"))
overall_data_exports_goods_services<-overall_data_exports_goods_services[-(1:10),]
colnames(overall_data_exports_goods_services)<-c("Date","Goods and services")
overall_data_exports_goods_services<-overall_data_exports_goods_services%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of overall data of US exports of goods
```{r}
overall_data_exports_goods<-read_excel(here::here("IEAXG.xls"))
overall_data_exports_goods<-overall_data_exports_goods[-(1:10),]
colnames(overall_data_exports_goods)<-c("Date","Goods")
overall_data_exports_goods<-overall_data_exports_goods%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of overall data of US exports of services
```{r}
overall_data_exports_services<-read_excel(here::here("IEAXS.xls"))
overall_data_exports_services<-overall_data_exports_services[-(1:10),]
colnames(overall_data_exports_services)<-c("Date","Services")
overall_data_exports_services<-overall_data_exports_services%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the above three data sets
```{r}
Overall<-left_join(overall_data_exports_goods_services,overall_data_exports_goods)
Overall<-left_join(Overall,overall_data_exports_services)
Overall<-Overall%>%
  gather(key=Name,value=Value,-Date)%>%
  mutate(Name=forcats::fct_reorder2(Name,Date,Value))%>%
  mutate(Value=as.numeric(Value))
```

### Analysis of General merchandise in the exports of U.S.

Transformation of the data of general merchandise
```{r}
general_merchandise<-read_excel(here::here("IEAXGM.xls"))
general_merchandise<-general_merchandise[-(1:10),]
colnames(general_merchandise)<-c("Date","General_merchandise")
general_merchandise<-general_merchandise%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the data sets of general merchandise and goods
```{r}
Overall_goods_general_merchandise<-left_join(overall_data_exports_goods,general_merchandise)
Overall_goods_general_merchandise<-Overall_goods_general_merchandise%>%
  gather(key=Name,value=Value,-Date)%>%
  mutate(Name=forcats::fct_reorder2(Name,Date,Value))%>%
  mutate(Value=as.numeric(Value))
```

Transformation of the data of general merchandise: Automotive vehicles, parts, and engines 
```{r}
gm_avpe<-read_excel(here::here("IEAXGAV.xls"))
gm_avpe<-gm_avpe[-(1:10),]
colnames(gm_avpe)<-c("Date","GM_AVPE")
gm_avpe<-gm_avpe%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Capital goods except automotive 
```{r}
gm_capital<-read_excel(here::here("IEAXGC.xls"))
gm_capital<-gm_capital[-(1:10),]
colnames(gm_capital)<-c("Date","GM_capital")
gm_capital<-gm_capital%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Consumer goods except food and automotive
```{r}
gm_consumer_goods<-read_excel(here::here("IEAXGCG.xls"))
gm_consumer_goods<-gm_consumer_goods[-(1:10),]
colnames(gm_consumer_goods)<-c("Date","GM_consumer_goods")
gm_consumer_goods<-gm_consumer_goods%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Foods, feeds, and beverages
```{r}
gm_food_feeds_beverages<-read_excel(here::here("IEAXGF.xls"))
gm_food_feeds_beverages<-gm_food_feeds_beverages[-(1:10),]
colnames(gm_food_feeds_beverages)<-c("Date","Gm_food_feeds_beverages")
gm_food_feeds_beverages<-gm_food_feeds_beverages%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Industrial supplies and materials
```{r}
gm_industrial_supplies_materials<-read_excel(here::here("IEAXGI.xls"))
gm_industrial_supplies_materials<-gm_industrial_supplies_materials[-(1:10),]
colnames(gm_industrial_supplies_materials)<-c("Date","Gm_industrial_supplies_materials")
gm_industrial_supplies_materials<-gm_industrial_supplies_materials%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the above 5 data sets
```{r}
Different_types_of_GM<-left_join(gm_avpe,gm_capital)%>%
  left_join(.,gm_consumer_goods)%>%
  left_join(.,gm_food_feeds_beverages)%>%
  left_join(.,gm_industrial_supplies_materials)%>%
  mutate(GM_AVPE=as.numeric(GM_AVPE))%>%
  mutate(GM_capital=as.numeric(GM_capital))%>%
  mutate(GM_consumer_goods=as.numeric(GM_consumer_goods))%>%
  mutate(Gm_food_feeds_beverages=as.numeric(Gm_food_feeds_beverages))%>%
  mutate(Gm_industrial_supplies_materials=as.numeric(Gm_industrial_supplies_materials))

Different_types_of_GM_new<-Different_types_of_GM%>%
  gather(key=Type,value=Value,-Date)%>%
  mutate(Type=forcats::fct_reorder2(Type,Date,Value))%>%
  mutate(Value=as.numeric(Value))
  
```

Create the index to compare the trends among different merchandise
```{r}
Different_types_of_GM_Index<-Different_types_of_GM_new%>%
  group_by(Type)%>%
  mutate(Index=round(100*Value/Value[1],2))%>% 
  ungroup()
```

## Question 2 Analyze the data of export cooperation between the United States and different countries

Introduce all of these data to take the first good look of them
```{r}
# Islands and areas within the United States
library(tidyverse)
goods_island <- read_csv(here::here("exports_goods_us_island.csv"))
manu_island <- read_csv(here::here("manufactured_commodity_us_island.csv"))
nonmanu_island <- read_csv(here::here("nonmanufactured_commodity_us_island.csv"))

goods_pr <- read_csv(here::here("exports_goods_puerto_rico.csv"))
manu_pr <- read_csv(here::here("manufactured_commodity_puerto_rico.csv"))
nonmanu_pr <- read_csv(here::here("nonmanufactured_commodity_puerto_rico.csv"))

# Countries bordering the United States
canada_goods <- read_csv(here::here("export_goods_canada.csv"))
mexico_goods <- read_csv(here::here("export_goods_mexico.csv"))

# Countries in Europe
france_goods <- read_csv(here::here("export_goods_france.csv"))
germany_goods <- read_csv(here::here("export_goods_germany.csv"))

# Countries in Asia
japan_goods <- read_csv(here::here("export_goods_japan.csv"))
korea_goods <- read_csv(here::here("export_goods_korea.csv"))
```

Basic transformations of data frame
```{r}
# Island data
goods_island <- goods_island %>%
  rename(Date = DATE, goods_island = EXPTOTVI)
manu_island <- manu_island %>%
  rename(Date = DATE, manufactured_island = EXPMANVI)
nonmanu_island <- nonmanu_island %>%
  rename(Date = DATE, nonmanufactured_island = EXPNONVI)
nonmanu_island$nonmanufactured_island <- as.numeric(nonmanu_island$nonmanufactured_island)

# Puerto Rico data
goods_pr <- goods_pr %>%
  rename(Date = DATE, goods_pr = EXPTOTPR)
manu_pr <- manu_pr %>%
  rename(Date = DATE, manufactured_pr = EXPMANPR)
nonmanu_pr <- nonmanu_pr %>%
  rename(Date = DATE, nonmanufactured_pr = EXPNONPR)

# Canada and Mexico data
canada_goods <- canada_goods %>%
  rename(Date = DATE, goods_canada = EXPCA)
mexico_goods <- mexico_goods %>%
  rename(Date = DATE, goods_mexico = EXPMX)

# Germany and France data
germany_goods <- germany_goods %>%
  rename(Date = DATE, goods_germany = EXPGE)
france_goods <- france_goods %>%
  rename(Date = DATE, goods_france = EXPFR)

# Japan and Korea data
japan_goods <- japan_goods %>%
  rename(Date = DATE, goods_japan = EXPJP)
korea_goods <- korea_goods %>%
  rename(Date = DATE, goods_korea = EXPKR)
```

Join different data frames to create new data - Type I data about islands and areas within the United States
```{r}
# Island data
island_dat <- goods_island %>%
  left_join(manu_island) %>%
  left_join(nonmanu_island)

# Puerto Rico data
pr_dat <- goods_pr %>%
  left_join(manu_pr) %>%
  left_join(nonmanu_pr)

# Type I data - Islands and areas within the United States
data <- island_dat %>%
  left_join(pr_dat)
data1 <- data %>%
  pivot_longer(cols = 2:7, names_to = "Type", values_to = "Value") %>%
  mutate(location = ifelse(str_detect(Type, "island"), "US Island", "Puerto Rico"))
```

Join different data frames to create new data - Type II data about countries bordering the United States
```{r}
data2_temp <- canada_goods %>%
  left_join(mexico_goods)
data2 <- data2_temp %>%
  pivot_longer(cols = 2:3, names_to = "Type", values_to = "Value") %>%
  mutate(location = ifelse(str_detect(Type, "canada"), "Canada", "Mexico"))
```

Join different data frames to create new data - Type III data about countries in Europe
```{r}
data3_temp <- france_goods %>%
  left_join(germany_goods)
data3 <- data3_temp %>%
  pivot_longer(cols = 2:3, names_to = "Type", values_to = "Value") %>%
  mutate(location = ifelse(str_detect(Type, "france"), "France", "Germany"))
```

Join different data frames to create new data - Type IV data about countries in Asia
```{r}
data4_temp <- japan_goods %>%
  left_join(korea_goods)
data4 <- data4_temp %>%
  pivot_longer(cols = 2:3, names_to = "Type", values_to = "Value") %>%
  mutate(location = ifelse(str_detect(Type, "japan"), "Japan", "South Korea"))
```

## Question3: Analyze U.S. export data to China

Transformation of the data of U.S. Exports of Goods by F.A.S. Basis to Mainland China
```{r}
library(readxl)
Exports_Mainland_China<-read_excel(here::here("EXPCH.xls"))
Exports_Mainland_China<-Exports_Mainland_China[-(1:10),]
colnames(Exports_Mainland_China)<-c("Date","Exports_Mainland_China")
Exports_Mainland_China<-Exports_Mainland_China%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))%>%
  mutate(Exports_Mainland_China=as.numeric(Exports_Mainland_China))
```

Transformation of the data of U.S. Imports of Goods by Customs Basis from China
```{r}
Imports_China<-read_excel(here::here("IMPCH-2.xls"))
Imports_China<-Imports_China[-(1:10),]
colnames(Imports_China)<-c("Date","Imports_China")
Imports_China<-Imports_China%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))%>%
  mutate(Imports_China=as.numeric(Imports_China))
```
 
Join the data sets of U.S. imports from China and U.S. exports to China
```{r}
Ex_Im_China<-left_join(Exports_Mainland_China,Imports_China)

Ex_Im_China_new<-Ex_Im_China%>%
  gather(key=Type,value=Value,-Date)%>%
  mutate(Type=forcats::fct_reorder2(Type,Date,Value))
  
```
