# Data transformation

## Question1: Analyze the development process of U.S. export data

### Overall trend in data of exports of goods and services

Transformation of overall data of US exports of goods and services
```{r}
library(tidyverse)
library(readxl)
overall_data_exports_goods_services<-read_excel(here::here("IEAXGS.xls"))
overall_data_exports_goods_services<-overall_data_exports_goods_services[-(1:10),]
colnames(overall_data_exports_goods_services)<-c("Date","Goods and services")
overall_data_exports_goods_services<-overall_data_exports_goods_services%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of overall data of US exports of goods
```{r}
overall_data_exports_goods<-read_excel(here::here("IEAXG.xls"))
overall_data_exports_goods<-overall_data_exports_goods[-(1:10),]
colnames(overall_data_exports_goods)<-c("Date","Goods")
overall_data_exports_goods<-overall_data_exports_goods%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of overall data of US exports of services
```{r}
overall_data_exports_services<-read_excel(here::here("IEAXS.xls"))
overall_data_exports_services<-overall_data_exports_services[-(1:10),]
colnames(overall_data_exports_services)<-c("Date","Services")
overall_data_exports_services<-overall_data_exports_services%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the above three data sets
```{r}
Overall<-left_join(overall_data_exports_goods_services,overall_data_exports_goods)
Overall<-left_join(Overall,overall_data_exports_services)
Overall<-Overall%>%
  gather(key=Name,value=Value,-Date)%>%
  mutate(Name=forcats::fct_reorder2(Name,Date,Value))%>%
  mutate(Value=as.numeric(Value))
```

Transformation of the data of general merchandise
```{r}
general_merchandise<-read_excel(here::here("IEAXGM.xls"))
general_merchandise<-general_merchandise[-(1:10),]
colnames(general_merchandise)<-c("Date","General_merchandise")
general_merchandise<-general_merchandise%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the data sets of general merchandise and goods
```{r}
Overall_goods_general_merchandise<-left_join(overall_data_exports_goods,general_merchandise)
Overall_goods_general_merchandise<-Overall_goods_general_merchandise%>%
  gather(key=Name,value=Value,-Date)%>%
  mutate(Name=forcats::fct_reorder2(Name,Date,Value))%>%
  mutate(Value=as.numeric(Value))
```

Transformation of the data of general merchandise: Automotive vehicles, parts, and engines 
```{r}
gm_avpe<-read_excel(here::here("IEAXGAV.xls"))
gm_avpe<-gm_avpe[-(1:10),]
colnames(gm_avpe)<-c("Date","GM_AVPE")
gm_avpe<-gm_avpe%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Capital goods except automotive 
```{r}
gm_capital<-read_excel(here::here("IEAXGC.xls"))
gm_capital<-gm_capital[-(1:10),]
colnames(gm_capital)<-c("Date","GM_capital")
gm_capital<-gm_capital%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Consumer goods except food and automotive
```{r}
gm_consumer_goods<-read_excel(here::here("IEAXGCG.xls"))
gm_consumer_goods<-gm_consumer_goods[-(1:10),]
colnames(gm_consumer_goods)<-c("Date","GM_consumer_goods")
gm_consumer_goods<-gm_consumer_goods%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Foods, feeds, and beverages
```{r}
gm_food_feeds_beverages<-read_excel(here::here("IEAXGF.xls"))
gm_food_feeds_beverages<-gm_food_feeds_beverages[-(1:10),]
colnames(gm_food_feeds_beverages)<-c("Date","Gm_food_feeds_beverages")
gm_food_feeds_beverages<-gm_food_feeds_beverages%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Transformation of the data of general merchandise: Industrial supplies and materials
```{r}
gm_industrial_supplies_materials<-read_excel(here::here("IEAXGI.xls"))
gm_industrial_supplies_materials<-gm_industrial_supplies_materials[-(1:10),]
colnames(gm_industrial_supplies_materials)<-c("Date","Gm_industrial_supplies_materials")
gm_industrial_supplies_materials<-gm_industrial_supplies_materials%>%
  mutate(Date=as.numeric(Date))%>%
  mutate(Date=as.Date(Date,origin="1899-12-30"))
```

Join the above 5 data sets
```{r}
Different_types_of_GM<-left_join(gm_avpe,gm_capital)%>%
  left_join(.,gm_consumer_goods)%>%
  left_join(.,gm_food_feeds_beverages)%>%
  left_join(.,gm_industrial_supplies_materials)%>%
  mutate(GM_AVPE=as.numeric(GM_AVPE))%>%
  mutate(GM_capital=as.numeric(GM_capital))%>%
  mutate(GM_consumer_goods=as.numeric(GM_consumer_goods))%>%
  mutate(Gm_food_feeds_beverages=as.numeric(Gm_food_feeds_beverages))%>%
  mutate(Gm_industrial_supplies_materials=as.numeric(Gm_industrial_supplies_materials))

Different_types_of_GM_new<-Different_types_of_GM%>%
  gather(key=Type,value=Value,-Date)%>%
  mutate(Type=forcats::fct_reorder2(Type,Date,Value))%>%
  mutate(Value=as.numeric(Value))
  
```

Create the index to compare the trends among different merchandise
```{r}
Different_types_of_GM_Index<-Different_types_of_GM_new%>%
  group_by(Type)%>%
  mutate(Index=round(100*Value/Value[1],2))%>% 
  ungroup()
```









